How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-07 tse-paper/content.tex
Align big comparison plot
Fix captions

\subsection{Common Text Similarity (CTS)}
\label{sec:r:cts}
\begin{figure*}
\centering
    \textbf{Common Text Similarity (CTS)}\par\medskip
\begin{subfigure}[t]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
		\caption{Compared with the training set size.}
		\label{fig:recall-precision-examplecount-CTS}

\end{subfigure}\hspace{\fill}
\begin{subfigure}[t]{\columnwidth}
		\centering
				\includegraphics[width=\columnwidth,
				clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
		\caption{Compared with the number of structural categories
		in the
		training and test sets.}
		\label{fig:recall-precision-categorycount-CTS}
\end{subfigure}
\caption{Precision, recall and F$_{1}$-score of chunk
retrieval with Common Text Similarity (CTS)}
\end{figure*}

@@

\subsection{Keyword Search (KWS)}
\label{sec:r:kws}
\begin{figure*}
\centering
    \textbf{Keyword Search (KWS)}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
		\caption{Compared with the training set size.\\ \,}
    % top-aligning captions
		\label{fig:recall-precision-examplecount-KWS}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
		\caption{Compared with the number of structural categories
		in the
		training and test sets.}
		\label{fig:recall-precision-categorycount-KWS}
\end{subfigure}
\caption{Precision, recall and F$_{1}$-score of chunk retrieval with
Keyword Search (KWS)}
\end{figure*}

@@

\subsection{Program Synthesis by Example (PBE)}
\label{sec:r:pbe}
\begin{figure*}
\centering
    \textbf{Program Synthesis by Example (PBE)}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
				\caption{Precision, recall and
				F$_{1}$-score when PBE could synthesize
				a consistent program compared with the
				size of the training set.}
		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
				\caption{Successfulness of retrieval
				compared with the number of
	structural categories in the training and test sets.}
		\label{fig:failure-reason-categorycount-PBE}
\end{subfigure}
\caption{Results of chunk retrieval with  Program Synthesis by Example
(PBE)}
\end{figure*}

@@

\begin{figure*}
\centering
    \textbf{PBE, CTS, KWS, and RLR}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
				\includegraphics[width=\columnwidth,
				clip]{img/big-study/recall-precision-singlecategory-all.pdf}
		\caption{Training and test examples are in \emph{one}
		structural category.\\ \,}
    % top-aligning captions
		\label{fig:recall-precision-singlecategory-all}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
				\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-multicategory-all.pdf}
		\caption{Training and test examples in \emph{more than
		one} structural categories.}
		\label{fig:recall-precision-multicategory-all}
\end{subfigure}
\caption{Precision, recall and F$_{1}$-score of all
techniques compared, split by structural category count.}
\end{figure*}

>>>>

\subsection{Common Text Similarity (CTS)}
\label{sec:r:cts}
\begin{figure*}
\centering
    \textbf{Common Text Similarity (CTS)}\par\medskip
\begin{subfigure}[t]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
		\caption{training set size.}
		\label{fig:recall-precision-examplecount-CTS}

\end{subfigure}\hspace{\fill}
\begin{subfigure}[t]{\columnwidth}
		\centering
				\includegraphics[width=\columnwidth,
				clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
		\caption{structural category count
		in training and test set.}
		\label{fig:recall-precision-categorycount-CTS}
\end{subfigure}
\caption{Precision, recall and F$_{1}$-score of chunk
retrieval with Common Text Similarity (CTS) compared by \ldots}
\end{figure*}

@@

\subsection{Keyword Search (KWS)}
\label{sec:r:kws}
\begin{figure*}
\centering
    \textbf{Keyword Search (KWS)}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
		\caption{training set size.\\ \,}
    % top-aligning captions
		\label{fig:recall-precision-examplecount-KWS}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
		\caption{structural category count
		in training and test sets.}
		\label{fig:recall-precision-categorycount-KWS}
\end{subfigure}
\caption{Precision, recall and F$_{1}$-score of chunk retrieval with
Keyword Search (KWS) compared by \ldots}
\end{figure*}

@@

\subsection{Program Synthesis by Example (PBE)}
\label{sec:r:pbe}
\begin{figure*}
\centering
    \textbf{Program Synthesis by Example (PBE)}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
				\caption{Precision, recall and
				F$_{1}$-score when PBE could synthesize
				a consistent program compared with the
				size of the training set.}
		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
				\caption{Successfulness of retrieval
				compared by structural category count in training and test sets.}
		\label{fig:failure-reason-categorycount-PBE}
\end{subfigure}
\caption{Results of chunk retrieval with  Program Synthesis by Example
(PBE)}
\end{figure*}

@@

\begin{figure*}
\centering
    \textbf{PBE, CTS, KWS, and RLR}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
				\includegraphics[width=\columnwidth,
				clip]{img/big-study/recall-precision-singlecategory-all.pdf}
		\caption{Training and test examples are in \emph{one}
		structural category.\\ \,}
    % top-aligning captions
		\label{fig:recall-precision-singlecategory-all}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
				\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-multicategory-all.pdf}
		\caption{Training and test examples are in $>1$ structural
		category.}
		\label{fig:recall-precision-multicategory-all}
\end{subfigure}
\caption{Precision, recall and F$_{1}$-score of all
techniques compared, split by structural category count.}
\end{figure*}
